The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-08-05 dit-paper_ieee.tex
Figure 5 correction moved figure 1 to /figs directory cleanup
Added Mr. Goossens as an authors small typos

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George and ???}
\IEEEauthorblockA{ECE Paris\\
lgeorge@ece.fr}
}
\maketitle

\begin{abstract}
Sensitivity analysis for real-time systems provides for efficient methods to determine feasibility
conditions  in the case of small changes in task parameters, such as when porting a system to a
different platform. The C-space, presented in \cite{bini2004schedulability,george2009characterization}, describes the
set of execution times for which a system is feasible. This paper extends previous works to
generalize the description of the C-space for Earliest Deadline First scheduling to
systems with initial offset. The feasibility gain offered by offsets is then
expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
synchronous system.
\end{abstract}

@@

  To summarize, we reduced the description of the C-space from an infinite number
  of constraints to only those where $t_1 = 0$, $t_2 \leqslant t_d$ and
  values of $t_2$ correspond to job deadlines. Note that the number of
  constraints is still exponential in the number of tasks.

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

@@

The general problem of redundancy of a new linear constraint $C \, X \leq d$ w.r.t. a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the following ILP:

\begin{figure}[h]
$$z = \max C \, X$$
s.t.
\[
\begin{array}{rccc}
  A & X &\leq & B \\
  C & X &\leq & d + 1
\end{array}
\]
with
\[
  \begin{array}{ccc}
    A & : & [n,k] \text{ matrix}\\
    B & : & [n,1] \text{ matrix}\\
    C & : & [n,1] \text{ matrix}\\
    X & : & [1,n] \text{ matrix}\\
    d & : & \text{integer}
  \end{array}
\]
\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
\end{figure}

>>>>

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George}
\IEEEauthorblockA{ECE Paris\\
lgeorge@ece.fr}
\and
\IEEEauthorblockN{Jo\e"l Goossens}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
joel.goossens@ulb.ac.be}
}
\maketitle

\begin{abstract}
Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
conditions  in the case of small changes in task parameters, such as when porting a system to a
different platform. The C-space, presented in \cite{bini2004schedulability,george2009characterization}, describes the
set of execution times for which a system is feasible. This paper extends previous works to
generalize the description of the C-space for Earliest Deadline First scheduling to
systems with initial offset. The feasibility gain offered by offsets is then
expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
synchronous system.
\end{abstract}

@@

  To summarize, we reduced the description of the C-space from an infinite number
  of constraints to only those where $t_1 = 0$, $t_2 \leqslant t_d$ and
  values of $t_2$ correspond to job deadlines. Note that the number of
  constraints is still exponential in the number of tasks in the worst-case ($t_d = H$).

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figs/nofpdit_3.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

@@

The general problem of redundancy of a new linear constraint $C \, X \leq d$ w.r.t. a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the ILP presented in Fig.~\ref{fig:redILP}.

\begin{figure}[h]
$$z = \max C \, X$$
s.t.
\[
\begin{array}{rccc}
  A & X &\leq & B \\
  C & X &\leq & d + 1
\end{array}
\]
with
\[
  \begin{array}{ccc}
    A & : & [n,k] \text{ matrix}\\
    B & : & [n,1] \text{ matrix}\\
    C & : & [n,1] \text{ matrix}\\
    X & : & [1,n] \text{ matrix}\\
    d & : & \text{integer}
  \end{array}
\]
\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
\label{fig:redILP}
\end{figure}
